Development and assessment of automated forest road projection methods using performance metrics relevant for wildlife

### 2024-06-12 analysis/paper/paper.Rmd
Add alt text

@@

Figure 2: Proportional difference of projected mean from observed mean road metrics using different projection method variants within cutblocks, outside cutblocks, and overall (1 ha weight raster). Values greater than zero indicate overprojection and negative values indicate underprojection. Cutblocks not accessible via the observed road network were excluded from analysis. Performance varies among metrics (columns), projection method variants (colours), and within and outside cutblocks. Projection method variants are defined in Table 2. Note that extreme values for the cutblocks only method within cutblocks are cut off to ensure patterns in the other methods to remain visible. Bars that are cutoff are labeled with the total value.

@@

@@

```{r proj-map-fig, fig.height=9, fig.width=fig_widths["two"], fig.cap="."}

@@

```{r spat-perf-fig, fig.height=4.5, fig.width=fig_widths["two"], out.width=paste0(fig_widths["two"], "in"), out.height="4.5in", fig.cap="."}

>>>>

Alt text: Two raster maps of Revelstoke timber supply area in grey scale, with an inset map showing the location of the study area within Canada.

@@

Figure 2: Proportional difference of projected mean from observed mean road metrics using different projection method variants within cutblocks, outside cutblocks, and overall (1 ha weight raster). Values greater than zero indicate overprojection and negative values indicate underprojection. Cutblocks not accessible via the observed road network were excluded from analysis. Performance varies among metrics (columns), projection method variants (colours), and within and outside cutblocks. Projection method variants are defined in Table 2. Note that extreme values for the cutblocks only method within cutblocks are cut off to ensure patterns in the other methods to remain visible. Bars that are cutoff are labeled with the total value. 
Alt text: A faceted bar chart with one bar for each projection method variant and a panel for each combination of performance metrics and within cutblock, outside cutblock and overall.

@@

Alt text: A series of 8 maps showing roads projected with different method variants.

@@

Alt text: A raster map of the Revelstoke TSA where the colour indicates the difference between obeserve and projected distance to road. Three inset maps zoom in of specific areas with Google satelite imagery in the background.
```{r proj-map-fig, fig.height=9, fig.width=fig_widths["two"], fig.cap="."}

@@

Alt text: A faceted bar chart with one bar for each projection method variant and a panel for each combination of binary performance metrics and within cutblock, outside cutblock and overall.
```{r spat-perf-fig, fig.height=4.5, fig.width=fig_widths["two"], out.width=paste0(fig_widths["two"], "in"), out.height="4.5in", fig.cap="."}
